---
title: "Project in R"
author: "Lucas Oke"
date: "`r Sys.Date()`"
output:
  html_document:
    toc: true
    df_print: paged
  word_document: default
  pdf_document:
    keep_tex: yes
editor_options: 
  chunk_output_type: inline
---

```{r include=FALSE}
# Required libraries
library(readxl)
library(ggplot2)
library(dplyr)
library(shiny)
library(plotrix)
library(corrplot) 
library(randomcoloR)
library(vcd)
library(tinytex)
library(DT)
library(knitr)
library(moments)
library(latticeExtra)
library(lestat)
library(echarts4r)
library(GGally)
library(caret)
library(shinydashboard)
```

Find out data [here](https://www.kaggle.com/fedesoriano/heart-failure-prediction).

Lets import those interesting data...

```{r include=FALSE}
cvadata = read_excel("C:/Users/hp/Dropbox (Ancien)/PC/Desktop/Project in R/CVADatabase.xlsx")
#Set HeartDisease as character
cvadata$HeartDisease <- as.factor(cvadata$HeartDisease)
#Set Oldpeak as numeric
cvadata$Oldpeak <- as.numeric(cvadata$Oldpeak)
attach(cvadata)
```

## DESCRIPTIVE STATISTICS

### Parameters Calculation

Let's compute the summary...

```{r}
Summary = summary(cvadata)
kable(Summary)
```

### Graphical Representation

#### Age

Trying visualization with e_chart...

```{r}
cvadata |>
  e_charts() |>
  e_histogram(Age, name = "Age", breaks = 10) |>
  e_density(Age, areaStyle = list(opacity = .4), smooth = TRUE, name = "Density", y_index = 1) |>
  e_tooltip(trigger = "axis")
```

#### Sex

```{r}
par(mfrow =c(1,2))
pie(table(Sex),
      col = hcl.colors(length(table(Sex)), "Spectral"),
      labels = c(0,1),
      main = paste("Sex Piechart")
      )
barplot(table(Sex), col = hcl.colors(length(table(Sex)), "Spectral"),
        main = paste("Sex Barplot"))
```

#### ChestPainType

```{r}
par(mfrow =c(1,2))
pie(table(ChestPainType),
      col = hcl.colors(length(table(ChestPainType)), "Spectral"),
      labels = c("ASY","NAP","ATA","TA" ),
      main = paste("ChestPainType Piechart")
      )
barplot(table(ChestPainType), col = hcl.colors(length(table(ChestPainType)), "Spectral"),
        main = paste("ChestPainType Barplot"))
```

#### RestingBP

```{r}
cvadata |>
  e_charts() |>
  e_histogram(RestingBP, name = "RestingBP", breaks = 10) |>
  e_density(RestingBP, areaStyle = list(opacity = .4), smooth = TRUE, name = "Density", y_index = 1) |>
  e_tooltip(trigger = "axis")
```

#### Cholesterol

```{r}
ggplot(cvadata, aes(x=Cholesterol))+
  geom_histogram(aes(y=..density..), color="black", fill="white", binwidth=10)+
  geom_density(alpha=.2, fill = "#FF6666")
```

#### FastingBS

```{r}
par(mfrow =c(1,2))
pie(table(FastingBS),
      col = hcl.colors(length(table(FastingBS)), "Spectral"),
      labels = c(0,1),
      main = paste("FastingBS Piechart")
      )
barplot(table(FastingBS), col = hcl.colors(length(table(FastingBS)), "Spectral"),
        main = paste("FastingBS Barplot"))
```

#### RestingECG

```{r}
par(mfrow =c(1,2))
pie(table(RestingECG),
      col = hcl.colors(length(table(RestingECG)), "Spectral"),
      labels = c("LHV","Normal","ST"),
      main = paste("RestingECG Piechart")
      )
barplot(table(RestingECG), col = hcl.colors(length(table(RestingECG)), "Spectral"),
        main = paste("RestingECG Barplot"))
```

#### MaxHR

```{r}
ggplot(cvadata, aes(x=MaxHR))+
  geom_histogram(aes(y=..density..), color="black", fill="white", binwidth = 10)+
  geom_density(alpha=.2, fill = "#FF6666")
```

#### ExerciseAngina

```{r}
par(mfrow =c(1,2))
pie(table(ExerciseAngina),
      col = hcl.colors(length(table(ExerciseAngina)), "Spectral"),
      labels = c("Y","N"),
      main = paste("ExerciseAngina Piechart")
      )
barplot(table(ExerciseAngina), col = hcl.colors(length(table(ExerciseAngina)), "Spectral"),
        main = paste("ExerciseAngina Barplot"))
```

#### Oldpeak

```{r}
ggplot(cvadata, aes(x=Oldpeak))+
  geom_histogram(aes(y=..density..), color="black", fill="white")+
  geom_density(alpha=.2, fill = "#FF6666")
```

#### ST_Slope

```{r}
cvadata%>%
ggplot(mapping =  aes(x= ST_Slope))+
  geom_bar()
```

#### HeartDisease

```{r}
cvadata%>%
ggplot(mapping =  aes(x= HeartDisease))+
  geom_bar()
```

## Association of 2 variables

Checking correlation in between the parameters...

```{r}
cvadata <- cvadata %>%
  mutate_if(is.character, as.factor)
cvadata_numeric = data.frame(Age,RestingBP,Cholesterol,MaxHR,Oldpeak)
acorr = cor(cvadata_numeric)
corrplot(acorr, type="lower", tl.col="black", tl.srt=45)
```

```{r eval=FALSE, include=FALSE}
ggpairs(cvadata, title = "correlogram with ggpairs()")
```

## Logistic Regression

```{r}
modele_reg <- glm(HeartDisease~ Age + Sex + ChestPainType + RestingBP + Cholesterol + FastingBS + 
                    RestingECG + MaxHR + ExerciseAngina + Oldpeak + ST_Slope,
                  data = cvadata, family = binomial())
summary(modele_reg)
```
