---
title: "Project in R"
author: "Lucas Oke"
output:
  html_document:
    df_print: paged
  word_document: default
  pdf_document:
    keep_tex: yes
runtime: shiny
---

```{r include=FALSE}
# Required libraries
library(readxl)
library(ggplot2)
library(dplyr)
library(shiny)
library(plotrix)
library(corrplot)
library(randomcoloR)
library(vcd)
library(tinytex)
library(DT)
library(knitr)
library(moments)
library(latticeExtra)
library(lestat)
library(echarts4r)
library(GGally)
library(caret)
library(shinydashboard)
```

Find out data [here](https://www.kaggle.com/fedesoriano/heart-failure-prediction).

Lets import those interesting data...

```{r include=FALSE}
cvadata = read_excel("C:/Users/hp/Dropbox (Ancien)/PC/Desktop/Project in R/CVADatabase.xlsx")
#Set HeartDisease as character
cvadata$HeartDisease <- as.factor(cvadata$HeartDisease)
#Set Oldpeak as numeric
cvadata$Oldpeak <- as.numeric(cvadata$Oldpeak)
attach(cvadata)
```

## DESCRIPTIVE STATISTICS

### Parameters Calculation

Let's compute the summary...

```{r}
Summary = summary(cvadata)
kable(Summary)
```

### Graphical Representation

#### Age

Trying visualization with e_chart...

```{r}
cvadata |>
  e_charts() |>
  e_histogram(Age, name = "Age", breaks = 10) |>
  e_density(Age, areaStyle = list(opacity = .4), smooth = TRUE, name = "Density", y_index = 1) |>
  e_tooltip(trigger = "axis")
```

#### Sex

```{r}
par(mfrow =c(1,2))
pie(table(Sex),
      col = hcl.colors(length(table(Sex)), "Spectral"),
      labels = c(0,1),
      main = paste("Sex Piechart")
      )
barplot(table(Sex), col = hcl.colors(length(table(Sex)), "Spectral"),
        main = paste("Sex Barplot"))
```

#### ChestPainType

```{r}
par(mfrow =c(1,2))
pie(table(ChestPainType),
      col = hcl.colors(length(table(ChestPainType)), "Spectral"),
      labels = c("ASY","NAP","ATA","TA" ),
      main = paste("ChestPainType Piechart")
      )
barplot(table(ChestPainType), col = hcl.colors(length(table(ChestPainType)), "Spectral"),
        main = paste("ChestPainType Barplot"))
```

#### RestingBP

```{r}
cvadata |>
  e_charts() |>
  e_histogram(RestingBP, name = "RestingBP", breaks = 10) |>
  e_density(RestingBP, areaStyle = list(opacity = .4), smooth = TRUE, name = "Density", y_index = 1) |>
  e_tooltip(trigger = "axis")
```

#### Cholesterol

```{r}
ggplot(cvadata, aes(x=Cholesterol))+
  geom_histogram(aes(y=..density..), color="black", fill="white", binwidth=10)+
  geom_density(alpha=.2, fill = "#FF6666")
```

#### FastingBS

```{r}
par(mfrow =c(1,2))
pie(table(FastingBS),
      col = hcl.colors(length(table(FastingBS)), "Spectral"),
      labels = c(0,1),
      main = paste("FastingBS Piechart")
      )
barplot(table(FastingBS), col = hcl.colors(length(table(FastingBS)), "Spectral"),
        main = paste("FastingBS Barplot"))
```

#### RestingECG

```{r}
par(mfrow =c(1,2))
pie(table(RestingECG),
      col = hcl.colors(length(table(RestingECG)), "Spectral"),
      labels = c("LHV","Normal","ST"),
      main = paste("RestingECG Piechart")
      )
barplot(table(RestingECG), col = hcl.colors(length(table(RestingECG)), "Spectral"),
        main = paste("RestingECG Barplot"))
```

#### MaxHR

```{r}
ggplot(cvadata, aes(x=MaxHR))+
  geom_histogram(aes(y=..density..), color="black", fill="white", binwidth = 10)+
  geom_density(alpha=.2, fill = "#FF6666")
```

#### ExerciseAngina

```{r}
par(mfrow =c(1,2))
pie(table(ExerciseAngina),
      col = hcl.colors(length(table(ExerciseAngina)), "Spectral"),
      labels = c("Y","N"),
      main = paste("ExerciseAngina Piechart")
      )
barplot(table(ExerciseAngina), col = hcl.colors(length(table(ExerciseAngina)), "Spectral"),
        main = paste("ExerciseAngina Barplot"))
```

#### Oldpeak

```{r}
ggplot(cvadata, aes(x=Oldpeak))+
  geom_histogram(aes(y=..density..), color="black", fill="white")+
  geom_density(alpha=.2, fill = "#FF6666")
```

#### ST_Slope

```{r}
cvadata%>%
ggplot(mapping =  aes(x= ST_Slope))+
  geom_bar()
```

#### HeartDisease

```{r}
cvadata%>%
ggplot(mapping =  aes(x= HeartDisease))+
  geom_bar()
```

## Association of 2 variables

```{r}
inputPanel(
  selectInput("variable1", "Numeric Variable", choices = c("Age", "RestingBP",
                                                   "Cholesterol", "FastingBS", "MaxHR",
                                                   "Oldpeak","HeartDisease" )),
  selectInput("variable2", "Variable", choices = names(cvadata))
)
 
renderPlot({
  boxplot(get(input$variable1) ~ get(input$variable2), data = cvadata, col = randomColor())
})
```

Checking correlation in between the parameters...

```{r}
cvadata <- cvadata %>%
  mutate_if(is.character, as.factor)
cvadata_numeric = data.frame(Age,RestingBP,Cholesterol,MaxHR,Oldpeak)
acorr = cor(cvadata_numeric)
corrplot(acorr, type="lower", tl.col="black", tl.srt=45)
```

```{r eval=FALSE, include=FALSE}
ggpairs(cvadata, title = "correlogram with ggpairs()")
```

## Logistic Regression

```{r}
modele_reg <- glm(HeartDisease~ Age + Sex + ChestPainType + RestingBP + Cholesterol + FastingBS + 
                    RestingECG + MaxHR + ExerciseAngina + Oldpeak + ST_Slope,
                  data = cvadata, family = binomial())
summary(modele_reg)
```

## Machine Learning model

```{r}
#Building a traing model:
## Random Forest
set.seed(10000)
fitControl = trainControl(method = "cv", number = 10)

ml_mod = train(HeartDisease~.,
                 data = cvadata,
                 method = "rf",
                 trControl = fitControl,
                 verbose = T)

#Save model in RDS:
saveRDS(ml_mod,"ML_mod.rds")
```

Let's shine a bit

```{r}
ui <- dashboardPage(
  dashboardHeader(title = "CVA Prediction"),
  
  dashboardSidebar(
    sidebarMenu(
      id = "tabs",
      menuItem("Correlation", tabName = "corr"),
      menuItem("Regression", tabName = "reg"),
      menuItem("Predict CVA occurence", tabName = "Predict_CVA_occurence"))
      
  ),
  
  dashboardBody(
    tabItems(
      tabItem("Predict_CVA_occurence",
      fluidRow(box(
      sliderInput("Age", label = "Age?", value = 28,
                                min = min(Age), max = max(Age)),
    sliderInput("RestingBP", label = "RestingBP", value = 0,
                                  min = min(RestingBP),
                                  max = max(RestingBP)),
    sliderInput("Cholesterol", label = "Cholesterol", value = 0,
                                  min = min(Cholesterol),
                                  max = max(Cholesterol)),
    sliderInput("MaxHR", label = "MaxHR", value = 60,
                                  min = min(MaxHR),
                                  max = max(MaxHR)),
    sliderInput("Oldpeak",label = "Oldpeak", value = 0,
                                  min = min(Oldpeak),
                                  max = max(Oldpeak))
    ),
    box(
        selectizeInput("Sex", label = "Sex", Sex),
    selectInput("ChestPainType", label = "ChestPainType", ChestPainType),
    numericInput("FastingBS", label = "FastingBS", value = 0,
                                   min = min(FastingBS),
                                   max = max(FastingBS)),
    selectInput("RestingECG", label = "RestingECG", RestingECG),
    selectInput("ExerciseAngina", label = "ExerciseAngina", ExerciseAngina),
    selectInput("ST_Slope", label = "ST_Slope", ST_Slope)
              )       
             ),
    fluidRow(valueBoxOutput("Occurence"))
    ),
    tabItem("reg", verbatimTextOutput('regression')),
    tabItem("corr",
      selectInput("variable1", "Numeric Variable", choices = c("Age", "RestingBP",
                                                   "Cholesterol", "FastingBS", "MaxHR",
                                                   "Oldpeak","HeartDisease" )),
      selectInput("variable2", "Variable", choices = names(cvadata)),
      plotOutput("corre")
    )
    )
    )
)

server <- function(input, output){
  
  prediction <- reactive({
    predict(
      ml_mod,
      data.frame("Age" = input$Age,
                 "Sex" = input$Sex,
                 "ChestPainType" = input$ChestPainType,
                 "RestingBP" = input$RestingBP,
                 "Cholesterol" = input$Cholesterol,
                 "FastingBS" = input$FastingBS,
                 "RestingECG"	= input$RestingECG,
                 "MaxHR"	= input$MaxHR,
                 "ExerciseAngina"	= input$ExerciseAngina,
                 "Oldpeak"	= input$Oldpeak,
                 "ST_Slope"	= input$ST_Slope
      ),
      type = "raw"
    )
  })
  prediction_label <- reactive({
    ifelse(prediction() == 0, "No AVC", "AVC")
  })
  prediction_prob <- reactive({
    predict(
      ml_mod,
      data.frame("Age" = input$Age,
                 "Sex" = input$Sex,
                 "ChestPainType" = input$ChestPainType,
                 "RestingBP" = input$RestingBP,
                 "Cholesterol" = input$Cholesterol,
                 "FastingBS" = input$FastingBS,
                 "RestingECG"	= input$RestingECG,
                 "MaxHR"	= input$MaxHR,
                 "ExerciseAngina"	= input$ExerciseAngina,
                 "Oldpeak"	= input$Oldpeak,
                 "ST_Slope"	= input$ST_Slope
      ),
      type = "prob"
    )
  })   
  prediction_color <- reactive({
    ifelse(prediction() == "0", "green", "red")
  })
  output$Occurence <- renderValueBox({
    valueBox( 
      paste0(round(100 * prediction_prob()$`1`, 0), "%"),
      prediction_label(),
      color = prediction_color()
    )
  })
  output$corre = renderPlot({
    boxplot(get(input$variable1) ~ get(input$variable2), data = cvadata, col = randomColor())
  })
  output$regression <- renderPrint({
    summary(modele_reg)
  })
}
shinyApp(ui, server)
```

## Project finished
